%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{jayme}{anchante}
       {data scientist}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    30 y.o.
    Porto Alegre
    Brazil
    ~
    \href{mailto:jayme.anchante@disroot.com}{email}
    \href{https://github.com/jaymeanchante/}{github}
    \href{https://www.linkedin.com/in/jaymeanchante}{linkedin}
    \href{https://www.kaggle.com/jaymeanchante}{kaggle}
  \section{languages}
    advanced portuguese, english, spanish
    basics of french and hebrew
  \section{programming}
    Python {\color{red} $\varheartsuit$} R
    Spark, mlflow
    SQL, shell, html, js
  \section{cloud}
    \hfill \break Microsoft Azure:
    Databricks, Data Factory, Logic
    Apps, Datalake
    
    \hfill \break Amazon Web Services:
    Elasticsearch, RDS Postgres, MySQL,
    S3, EC2 with GPUs
    
    \hfill \break Google Cloud Platform:
    BigQuery, Google Storage
\end{aside}

\section{interests}

experienced data professional, working with data engineering, data science,
machine learning, visualization, agile and cloud.

worked in the marketing team for a startup, created the analytics ecosystem
of a crm startup, presented data projects alongside the sales team

in the current experience deployed several models to production ranging from
sgementation, fraud detection, churn, forecasts, insights and analytics

recently, developing as a data science manager and agile practitioner

\section{education}

\begin{entrylist}
  \entry
    {2018-2019}
    {Specialization}
    {LEG e DInf/Federal University of Paraná}
    {\emph{Data Science and Big Data}}
  \entry
    {2015–2017}
    {Masters}
    {DER/Federal University of Viçosa}
    {Applied Economics}
  \entry
    {2009–2014}
    {Bachelors}
    {DERI/Federal University of Rio Grande do Sul}
    {Economics}
\end{entrylist}

\section{professional experiences}

\begin{entrylist}
  \entry
    {apr/2020 - }
    {\href{https://www.edenred.com}{Edenred}, Paris}
    {Staff data scientist - 2020/2021, Data science manager - 2022}
    {Began working as a consultant for the analytics of a fleet management platform.
    As a staff data scientist, deployed several models to production and supervised junior analysts.
    As data science manager is overseeing a team of 4 data scientists}
  \entry
    {jul/2018 - mar/2020}
    {\href{https://www.4all.com/}{4all tecnologia}, Porto Alegre}
    {Senior data scientist}
    {Development of machine learning algorithms for a Customer Data Platform.
    Lead data scientist in enterprise cutting edge customer algorithms for the retail, industrial and financial sectors.
    Data evangelist: speaker in internal and external meetups, instructor at workshops}
  \entry
    {oct/2017 - jul/2018}
    {\href{https://www.contabilizei.com.br}{Contabilizei Contabilidade}, Curitiba}
    {Junior data scientist}
    {Data processing and development of financial information classification algorithm.
    Marketing lead classification and scoring.
    Time series predictive modelling of page views, clicks and sales.
    Dashboards, visualizations and reports to analysts and C-levels.}
  \entry
    {mar/2015 - mar/2017}
    {\href{cnpq.br}{CNPq}, Viçosa}
    {Masters fellowship}
    {Applied Economic Research, econometric modelling using Stata, using government databases, Agriculture Derivatives course monitor.}
\end{entrylist}

\end{document}
